---
title: "Alcohol vs Seat choice"
author: "Isabela Bercian"
date: "Spring 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  We have three boxplots. The first boxplot, representing the back row, has a median that seems to land at 5. Comparing this to the box representing the front row, we can see that the median of the back row is higher than the third quirtile than the front. A similar thing is true about the boxplot representing the middle row. This omplies that there is a difference in the amount of people/drinks that are in the back, front and middle row. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The "bites" on the sides of the boxes represent standard deviation within those groups. There are bigger bites on the boxplot representing the back row. This group has more variation compared to the other two groups.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The Q1 of all boxplots is 0. However, Q3 shows the back row up at 12, and the front and middle rows at 2 and 4. There are 36 people sitting in the back row, which is less than both front and middle rows. The middle row has the most people in it at 89. This   

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The number 0.0001 inclines me to reject the null hypothesis. This is because 0.0001 shows that the chances of getting these results is far too low if nothing was happening. 

## Conclusions


